A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-06 latex/main.tex
Updates from Overleaf

%%%  All original research papers must include a
%%%  comprehensive and accurate ``data and code
%%%  availability'' statement within the ``resource
%%%  availability'' component of the paper before it
%%%  is accepted for publication. These statements
%%%  are structured and consist of three bulleted
%%%  components. Each component must be present.

[FIXME: fix the typesetting once all resources are compiled]

\begin{itemize}
\item The sequences alignments in VCF Zarr format have been deposited at Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The ARG in tskit format has been deposited at Zenodo and is publicly available at \url{https://zenodo.org/records/16313750}.
\item The complete configuration file for running sc2ts to build the ARG above is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original source code of sc2ts is publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts/}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

SHZ is supported by an NDPH Intermediate Research Fellowship
(Oxford Population Health, University of Oxford). JK and YW acknowledge support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation.

@@

\begin{table}
\caption{
RIPPLES events associated with Pango X lineages.
Each row is a recombination event identified by RIPPLEs (at p = 3)
in which Pango X lineages appear,
along with the corresponding sc2ts event from Table~\ref{tab:pango_x_lineages},
where applicable, grouped by class.
Events also present at p = 4 are indicated.
Clades are matched by finding the most recent common ancestor of
the samples associated with each UShER+RIPPLES event in the sc2ts ARG.
The clade differences indicates how close this match is.
}
\label{tab:ripples_x_lineages}
\centering
\begin{scriptsize}

>>>>

%%%  All original research papers must include a
%%%  comprehensive and accurate ``data and code
%%%  availability'' statement within the ``resource
%%%  availability'' component of the paper before it
%%%  is accepted for publication. These statements
%%%  are structured and consist of three bulleted
%%%  components. Each component must be present.
\begin{itemize}

\item The sequences alignments in VCF Zarr format have been deposited at Zenodo and are publicly available at \url{https://zenodo.org/records/16314739}.
\item The Snakemake workflow for aligning and converting the Viridian v05 dataset to VCF Zarr is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/viridian\_dataset/}.
\item The ARG in tskit format has been deposited at Zenodo and is publicly available at \url{https://zenodo.org/records/16313750}.
\item The complete configuration file for running sc2ts to build the ARG above is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/inference/viridian\_config.toml}.
\item The Snakemake workflow for ARG post-processing is publicly available at \url{https://github.com/jeromekelleher/sc2ts-paper/blob/main/arg_postprocessing/Snakefile}.
\item The original source code of sc2ts is publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts/}.
\item The Jupyter notebooks and the Mathematica script to perform the analyses in this paper are publicly available on GitHub at \url{https://github.com/jeromekelleher/sc2ts-paper/}.
\end{itemize}

@@

SHZ is supported by an NDPH Intermediate Research Fellowship
(Oxford Population Health, University of Oxford). 
% "ackknowledges support" here means "was awarded this grant 
% and it supported this research"
JK acknowledges support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation.

@@

\begin{table}
\caption{
RIPPLES events associated with Pango X lineages.
Each row is a recombination event identified by RIPPLEs (at $p=3$)
in which Pango X lineages appear,
along with the corresponding sc2ts event from Table~\ref{tab:pango_x_lineages},
where applicable, grouped by class.
Events also present at $p=4$ are indicated.
Clades are matched by finding the most recent common ancestor of
the samples associated with each UShER+RIPPLES event in the sc2ts ARG.
The clade differences indicates the closeness of the match.
}
\label{tab:ripples_x_lineages}
\centering
\begin{scriptsize}
